PK object batch mode trial

### 2023-08-01 data-raw/batchMode_trial_gpm.Rmd
Updated coef_sd method for batch mode.

# This is printable into a one file, multipage pdf
pdf(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/plotMethod_freeY.pdf",
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)
dev.off()

png(file = "C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Code Notes/examplePlot.png",
    width = 8,
    height = 6,
    units = "in",
    res = 150,
    type = "cairo",
    antialias = "none")
plot(my_pk, use_scale_conc = TRUE,
     method = "L-BFGS-B",
     print_out = TRUE)[[3]]
dev.off()

@@

@@

ggsave(paste0("C:/Users/GPADILLA/OneDrive - Environmental Protection Agency (EPA)/Profile/Documents/Figures/",
              "NormalizedConcentrations_2023-07-11.png"),
       height = 3.5,
       width = 5.5,
       units = "in")

@@

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-07-19.png"),
       height = 4,
       width = 6,
       units = "in")

@@

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "ModelPerformance_vDataVariability_2023-07-20.png"),
       height = 3.5,
       width = 7,
       units = "in")

@@

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "PredictedObserved_compartmentModels_2023-07-11.png"),
       height = 6, width = 7)

@@

ggsave(paste0("C:/Users/GPADILLA/",
              "OneDrive - Environmental Protection Agency (EPA)/",
              "Profile/Documents/Figures/",
              "OrdersOfMagnitude_2023-07-12.png"),
       height = 4, width = 4)

>>>>

# This is printable into a one file, multipage pdf
pdf(file = paste0(Sys.getenv("FIG_DIR"), "plotMethod_freeY.pdf"),
    width = 10,
    height = 8)
plot(my_pk, use_scale_conc = TRUE,
     print_out = TRUE)
dev.off()

@@

my_predata <- cvt %>%
  dplyr::filter(chemicals_analyzed.dsstox_substance_id %in% "DTXSID0020442")
my_pk <- pk(data = my_predata) +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  # scale_time(new_units = "auto") +
  # stat_model() + 
  stat_error_model(error_group = vars(Chemical, Species)) 
my_pk <- do_fit(my_pk)

my_hess <- coef_sd(my_pk)

my_hess %>%
  rowwise() %>%
  mutate(sds = list(sds))

@@

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "NormalizedConcentrations_2023-07-11.png"),
       height = 3.5,
       width = 5.5,
       units = "in")

@@

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ADME_NormalizedTime-NormalizedConcentrations_onlyDetects_2023-07-19.png"),
       height = 4,
       width = 6,
       units = "in")

@@

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "ModelPerformance_vDataVariability_2023-07-20.png"),
       height = 3.5,
       width = 7,
       units = "in")

@@

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "PredictedObserved_compartmentModels_2023-07-11.png"),
       height = 6, width = 7)

@@

ggsave(paste0(Sys.getenv("FIG_DIR"),
              "OrdersOfMagnitude_2023-07-12.png"),
       height = 4, width = 4)
